MachLensFinder - I: An automated Strong Lensing Identification Pipeline

### 2016-12-21 ms.tex
Modified sample lensed/unlensed images to be the same for HST, LSST, and stacked LSST

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]\label{fig:mockimages}
\begin{center}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1_color.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/105_unlensed_imgs_1_color.pdf}\\
\includegraphics[width=1\columnwidth]{figures/lsst_9_lensed_imgs_1_color.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/lsst_9_unlensed_imgs_1_color.pdf}
\caption{Top panel: Example mock HST images, with $n_\text{pix}\times
  n_\text{pix}=300\times300$.  The left corresponds to a strong
  gravitational lensing system with a visibly obvious giant arc.  The
  right corresponds to a non-lensing system.  Bottom panel: Example
  mock LSST images, with $n_\text{pix}\times n_\text{pix}=45\times45$.
  The resolution and noise of a ground based telescope is noticeably
  worse.  The left corresponds to a strong gravitational lensing
  system, and the right to a non-lensing system.  However, visual
  identification of giant arcs in the LSST images is very difficult.}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]\label{fig:mockimages}
\begin{center}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1_color.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/105_unlensed_imgs_1_color.pdf}\\
\includegraphics[width=1\columnwidth]{figures/lsst_105_lensed_imgs_1.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/lsst_105_unlensed_imgs_1.pdf}\\
\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_lensed_imgs_1.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/lsst_stack_105_unlensed_imgs_1.pdf}
\caption{Top row: Example mock HST images, with $n_\text{pix}\times
  n_\text{pix}=300\times300$.  The left corresponds to a strong
  gravitational lensing system with a visibly obvious giant arc.  The
  right corresponds to a non-lensing system.  Middle row: Example mock
  LSST images for a single epoch, with $n_\text{pix}\times
  n_\text{pix}=45\times45$.  The resolution and noise of a ground
  based telescope is noticeably worse.  The left and right images
  correspond to the same systems as the top row.  However, visual
  identification of giant arcs in the LSST images is very difficult.
  Bottom row: Example mock LSST images for stacked data over the 10
  year run.  Here, the arc is more visible, but not as well resolved
  as in the HST case.}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
